Approximation as Differentiation notes

### 2025-03-03 notes/sec/set-indexed-product.tex
Clarify set-indexed product diagram commutes for every in I.

$C$ \emph{has set-indexed products} if, for any set $I$ and any $I$-indexed family $X$ of objects of $C$,
there exists an object $\prod_{i \in I}X_i$ (also written $\prod_{I} X$) and family of morphisms $\eval_i$ in
$C$ such that for any object $Y$ and any family of morphisms $\{f_i: Y \to X_i\}_{i \in I}$ in $C$, there
exists a unique morphism $\lambda f$ making the following diagram commute:

>>>>

$C$ \emph{has set-indexed products} if, for any set $I$ and any $I$-indexed family $X$ of objects of $C$,
there exists an object $\prod_{i \in I}X_i$ (also written $\prod_{I} X$) and family of morphisms $\eval_i$ in
$C$ such that for any object $Y$ and any family of morphisms $\{f_i: Y \to X_i\}_{i \in I}$ in $C$, there
exists a unique morphism $\lambda f$ making the following diagram commute for every $i \in I$:
